SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-03 sedona-ieice16/revision/paper.tex
SEDONA updates

>>>>

{\color{blue}
We compared the performance of ORG and \hbox{SEDONA} on 
real programs such as insertion sort, termed SORT and 
matrix multiplication (in column major), termed MM. 
SEDONA overwhelmed ORG, as can be seen in Fig.~\ref{fig:synprog_test}. 
As workload size increased, 
the performance gap between SEDONA and ORG got increasingly widened, reaching up to by 6x.

\begin{figure}[htp!]
	\centering
	\subfigure[SORT - Standard Deviation]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[SORT - Relative Error]{
		\includegraphics[scale=0.31]{sort_re.eps}
		\label{fig:sort_re}
	}
	\subfigure[MM - Standard Deviation]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	\subfigure[MM - Relative Error]{
		\includegraphics[scale=0.31]{matc_re.eps}
		\label{fig:matc_re}
	}
	\vspace{-.1in}
	\caption{Performance Comparison on Real-world Programs~\label{fig:synprog_test}}
\vspace{-.2in}
\end{figure}
}
